Extension of the approximate static condensation method for multi-material diffusion problems to 3D

### 2019-08-08 3d/asc3d.tex
High order algorithm

\AZ{TBA: basic notations and quick problem setting.}
\begin{eqnarray}
	\arraycolsep=2pt\def\arraystretch{1.5}
	\left\{\begin{array}{rcrccl}
	\vect K^{-1}\,\vect u                   & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
	\nabla\cdot\vect u                      & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
											&   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
	\end{array}\right.
	& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
	& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
\end{eqnarray}
\begin{equation}\label{local}
	\begin{pmatrix}
		\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
		-\vect B_\mmesh & \vect \Sigma_\mmesh
	\end{pmatrix}
	\begin{pmatrix} {\vect u}_\mmesh \\ {\vect p}_\mmesh \end{pmatrix}
	=
	\begin{pmatrix} \vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\ {\vect f}_\mmesh \end{pmatrix}.
\end{equation}

@@

\AZ{I would much appreciate if somebody adds the description. Daniil, could you do this? :)}

>>>>

\AZ{TBA: basic notations and quick problem setting.}
\begin{eqnarray}
	\arraycolsep=2pt\def\arraystretch{1.5}
	\left\{\begin{array}{rcrccl}
	\vect K^{-1}\,\vect u                   & + & \nabla\,p & = & 0       &\quad\text{in } \bcell, \\
	\nabla\cdot\vect u                      & + & c\,p      & = & f       &\quad\text{in } \bcell, \\
											&   & p         & = & \lambda &\quad\text{on } \partial\bcell, %\label{dual_mini:trace}
	\end{array}\right.
	& \qquad \forall~\bcell\in\bmesh, \label{dual_mini} \\
		\llbracket\vect u \cdot \hat{\vect n}\rrbracket = 0\quad\:\:\text{on } F,\:\:\:\:
	& \qquad\quad \forall~F\in\bfaces[int]. \label{flux_cond}
\end{eqnarray}

In the weak form this problem is formulated as follows:
find $\vect u \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t. $\vect u \cdot \hat{\vect n} = g_N$ on $\partial\Omega_N$, $ p\in\LTwoSpace$, $\lambda\in\HHalfSpace[{\bfaces[int]}]$ such that
	\begin{equation}\label{weak_form}
		\begin{split}
			\int_{\Omega} \vect K^{-1}\,\vect u\cdot\vect v \diff \vect x - \sum_{\bcell\in\bmesh}\int_\bcell p\,\nabla\cdot\vect v \diff \vect x + \sum_{\bface\in\bfaces[int]}\int_{\bface} \lambda\,\llbracket\vect v\cdot\hat{\vect n}\rrbracket \diff l &= -\int_{\partial\Omega_D} g_D\,\vect v\cdot\hat{\vect n} \diff l, \\
			\sum_{\bcell\in\bmesh}\int_\bcell \nabla\cdot\vect u\,q \diff \vect x + \int_\Omega c\,p\,q \diff \vect x &= \int_\Omega f\,q \diff \vect x, \\
			\sum_{\bface\in\bfaces[int]}\int_{\bface} \llbracket\vect u\cdot\hat{\vect n}\rrbracket\,\mu \diff l &= 0
		\end{split}
	\end{equation}
	for all $\vect v \in \bigotimes\limits_{\bcell\in\bmesh}\HDivSpace[\bcell]$ s.t. $\vect v \cdot \hat{\vect n} = 0$ on $\partial\Omega_N$, $q \in \LTwoSpace[\Omega]$, and $\mu \in \HHalfSpace[{\bfaces[int]}]$.

        We shall discretize problem \eqref{weak_form} on a particular cell $T$ in terms of average fluxes assigned to each face from $\mfaces(T)$,
        we denote the corresponding vector by ${\vect u}_\mmesh\in\mathbb{R}^{n_f}$, $n_f=\#\mfaces(T)$,  and concentration values assigned to each cell ${\tau \in \mmesh(T)}$, we denote the corresponding vector by ${\vect p}_\mmesh\in\mathbb{R}^{n_p}$, $n_p=\#\mmesh(T)$. The given data is the source term vector ${\vect f}_\mmesh\in \mathbb{R}^{n_p}$ and the concentration values $\lambda$ on the boundary of $T$.
	To approximate this boundary data \emph{for the local problem}, we introduce the vector
	${\vect \lambda}_\mmesh\in\mathbb{R}^{n_\lambda}$, $n_\lambda=\#\mfaces[ext](T)$,
	where we assign one averaged concentration value for each $f\in\mfaces[ext](T)$, so that ${\vect \lambda}_\mmesh$ can be seen as a piecewise-constant approximation of $\lambda$ with respect to the subdivision of $\partial T$ into the faces of the local mesh $\mmesh$.

%Before we go into details of the method, we note that $\lambda$ can also  be observed as the Lagrange multiplier corresponding to the normal flux condition~\eqref{flux_cond}.
%The problem \eqref{dual_mini}--\eqref{flux_cond} can be formulated in the weak form:

\begin{equation}\label{local}
	\begin{pmatrix}
		\phantom{-}\vect M_\mmesh & \vect B^T_\mmesh \\
		-\vect B_\mmesh & \vect \Sigma_\mmesh
	\end{pmatrix}
	\begin{pmatrix} {\vect u}_\mmesh \\ {\vect p}_\mmesh \end{pmatrix}
	=
	\begin{pmatrix} \vect E_\mmesh\,\vect C_\mmesh\,{\vect \lambda}_\mmesh \\ {\vect f}_\mmesh \end{pmatrix}.
\end{equation}

\subsection{Lowest order method}

@@

%\AZ{I would much appreciate if somebody adds the description. Daniil, could you do this? :)}
Let $\vect s_{ji}$ are the vectors which connects the centoroid of macroface $F_j$ and
mini-faces $f_i$.
The matrix $S_j=\{ \vect s_{j1}, \vect s_{j2} \dots \vect s_{jn}\}$ for macroface $F_j$
is formed using $\vect s_{ji}$ as columns, $S_j \in {\mathbb R}^{3\times n}$. Since we assume
that all macrofaces are planar then $rank(S_j) \le 2$. For better readability of the formulas we droppped the subscript $j$ bellow.
Let consider $QR$ decomposition of matrix $S$. Since it is possible that $S$ has incomplete rank then:

$$ S P = QR=(\vect q_1, \vect q_2, \vect q_3)
\left(
\begin{array}{cc}
R_{11} & R_{12}\\
0 & 0
\end{array}
\right),$$

\noindent where $P$ is a permutation matrix, $Q \in \mathbb R^{3\times 3}$ is orthogonal matrix,
$R_{11}\in \mathbb R^{2\times 2}$ is uppper triangular matrix and $R_{12} \in \mathbb R^{2\times(n-2)}$.
For the sake of simplicity we assume that $P$ is identity matrix. This can be achieved by
the corresponding ordering of mini-faces $f_i$. Now we impose the continuity condition for the inteface fluxes we need to introduce the discrete space on macrofaces and establish
the relationship between degrees of freedom on mini and macrofaces. The degrees of freedom for $\lambda$ on minifaces are defined as :

$$\lambda(f_i) = \frac{1}{|f_i|}\int_{f_i} \lambda dx$$

If we introduce the average concentration on a macroface as one macroface degrees of freedom:

$$\lambda^{(0)}(F) = \frac{1}{|F|}\int_{F} \lambda dx$$

then $\lambda(f_i)$ can be expressed in terms of $\lambda(F)$ as follows:

$$\lambda(f_i) = \lambda^{(0)}(F) + \nabla^T \lambda \cdot \vect s_i$$
or
$$\lambda_f^T =  \lambda^{(0)}(F) \vect e^T + \nabla^T \lambda S =
\lambda^{(0)}(F) \vect e^T + \nabla^T \lambda (\vect q_1, \vect q_2, \vect q_3)
\left(
\begin{array}{cc}
R_{11} & R_{12}\\
0 & 0
\end{array}
\right) = $$
$$\lambda^{(0)}(F) \vect e^T  + (\nabla^T \lambda  \cdot  \vect q_1, \nabla^T \lambda  \cdot  \vect q_2) \left(
\begin{array}{cc}
R_{11} & R_{12}
\end{array}
\right) = \lambda^{(0)}(F) \vect e^T + (\lambda^{(1)}(F),\lambda^{(2)}(F)) \left(
\begin{array}{cc}
R_{11} & R_{12}
\end{array}
\right).$$

Here, the additional degrees of freedom $\lambda^{(k)}(F) = \nabla^T \lambda  \cdot  \vect q_k, k=1,2$
are introduced and $\vect e$ is the vector of ones.

To close the global linear system we neeed to impose the interface conditions for the fluxes $\vect u^{\text{ext}}_\mmesh$.

\begin{equation}\label{flux_cont1}
\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\, \diff s =
\int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\, \diff s, \text{for each } F \in \bfaces[int],
\end{equation}

\begin{equation}\label{flux_cont2}
\int_F \vect u|_{\bcell^+}\cdot\hat{\vect n}\,({\vect r} \cdot \vect q_k^{\bcell^+}) \diff s =
\int_F \vect u|_{\bcell^-}\cdot\hat{\vect n}\,({\vect r} \cdot \vect q_k^{\bcell^-}) \diff s,
\quad k=1,2,  \quad \text{for each } F \in \bfaces[int],
\end{equation}

where ${\vect r}^T = (x-x_F, y-y_F, z-z_F).$
